---
layout: post
title:  "Using the tree (drill-down) widget"
excerpt: "Display and manipulate a tree with Tk."
author: james_and_philippe
modified: 2015-12-23
categories: [recipes, tcltk]
section: "Additional widgets"
tags: [tcltk, GUI, programming]
image:
  feature: banner-tcltk.png
  credit: 
  creditlink: 
  teaser: banner-tcltk.png
comments: true
share: true
---

_Note: this has not been edited yet from the original form_

The tree widget from the BWidget package is useful for displaying hierarchical information. Because it can be drilled-down or drilled-up it can be a way to save space in a user-interface while still providing the user with all of the information that they need.

In the example below, we create a simple tree with four records (nodes), each containing two child nodes ("Name" and "Age"), each of which contains one child node, (the corresponding value for its parent node).

```{r, eval=FALSE}
library(tcltk2)
tclRequire("BWidget")

tt <- tktoplevel()
tkwm.title(tt, "Tree (Drill-Down) Widget")

xScr <- tkscrollbar(tt, command = function(...)
  tkxview(treeWidget, ...), orient = "horizontal")
yScr <- tkscrollbar(tt, command = function(...)
  tkyview(treeWidget, ...), orient = "vertical")
treeWidget <- tkwidget(tt, "Tree",
  xscrollcommand = function(...) tkset(xScr, ...),
  yscrollcommand = function(...) tkset(yScr, ...),
  width = 30, height = 15)
tkgrid(treeWidget, yScr)
tkgrid.configure(yScr, stick = "nsw")
tkgrid(xScr)
tkgrid.configure(xScr, stick = "new")

# Insert at the end of the nodes in "root" a new node, called
# "Record1Node", which displays the text "Record 1", etc.
tkinsert(treeWidget, "end", "root", "Record1Node", text = "Record 1")
tkinsert(treeWidget, "end", "root", "Record2Node", text = "Record 2")
tkinsert(treeWidget, "end", "root", "Record3Node", text = "Record 3")
tkinsert(treeWidget, "end", "root", "Record4Node", text = "Record 4")

tkinsert(treeWidget, "end", "Record1Node", "Name1Node", text = "Name")
tkinsert(treeWidget, "end", "Record2Node", "Name2Node", text = "Name")
tkinsert(treeWidget, "end", "Record3Node", "Name3Node", text = "Name")
tkinsert(treeWidget, "end", "Record4Node", "Name4Node", text = "Name")

tkinsert(treeWidget, "end", "Record1Node", "Age1Node", text = "Age")
tkinsert(treeWidget, "end", "Record2Node", "Age2Node", text = "Age")
tkinsert(treeWidget, "end", "Record3Node", "Age3Node", text = "Age")
tkinsert(treeWidget, "end", "Record4Node", "Age4Node", text = "Age")

tkinsert(treeWidget, "end", "Name1Node", "Name1Val", text = "Fred")
tkinsert(treeWidget, "end", "Name2Node", "Name2Val", text = "Jane")
tkinsert(treeWidget, "end", "Name3Node", "Name3Val", text = "Tim")
tkinsert(treeWidget, "end", "Name4Node", "Name4Val", text = "Alex")

tkinsert(treeWidget, "end", "Age1Node", "Age1Val", text = "14")
tkinsert(treeWidget, "end", "Age2Node", "Age2Val", text = "35")
tkinsert(treeWidget, "end", "Age3Node", "Age3Val", text = "63")
tkinsert(treeWidget, "end", "Age4Node", "Age4Val", text = "52")
```

 
The tree can be drilled down.


### Determining the currently selected node

An item in the tree can be selected by clicking with the mouse. To find out which node is currently selected, use:

```{r, eval=FALSE}
tclvalue(tkcmd(treeWidget, "selection", "get"))
## [1] "Age2Val"
```


### Deleting A Node

To delete a node (and all of its children), use:

```{r, eval=FALSE}
tkdelete(treeWidget, "Age1Node")
```

Now the age has been deleted from the first record.


### Images

The tree widget can also be used to display images, by using the image option in `tkinsert()` instead of the text option (not shown).
